Distributed Decision Making for Dynamic Formation of Web Services Communities

### 2015-01-19 papers/webservice-coalition-learning-omar-template/elsarticle-template-num.tex
changes

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Decision Support Systems}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Distributed Decision Making for Dynamic Formation of Web Services Communities}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{}

\address{}

\begin{abstract}
Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, existing community models mostly focus on short term goals. Moreover, these models generally suffer from high computational complexity, which makes decision making about community formation in real-time extremely hard, time consuming, and even impossible in some complex cases. In this paper, we propose a strategic distributed decision making mechanism called DDM that regulates web service agents' decision making process, which is about deciding with whom to cooperate. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our model helps 1) communities of web services efficiently find the appropriate web service to invite as new member; and 2) single web services find best communities to join. After being trained, web services get to compute expectations as utilities they would gain if cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated initiated by a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions. We performed experiments using real data from 142 users on 4,532 web services on 64 different time slots. The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
\end{abstract}

\begin{keyword}
Web services\sep Community of services\sep Distributed Decision Making
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}

\IEEEPARstart{O}{ver} the past years, online services have become an important part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue. One practical solution towards delivering high quality services is utilizing intelligent decision making agents. These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, journals/tsc/ZhengZYB13, Demirkan2013412}. However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided. Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals. In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals. To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}. A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

@@

\begin{table*}[ht]
\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
\centering % used for centering table
\scriptsize
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
 & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:nonlin} % is used to refer this table in the text
\end{table*}

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\bibliographystyle{elsarticle-num} 
\bibliography{Ehsan}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

%\bibitem{}

\end{thebibliography}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

>>>>

\documentclass[11pt,onecolumn]{IEEETran}

\usepackage{lineno,hyperref}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{url}\renewcommand{\baselinestretch}{1}
\usepackage{epsfig}
\usepackage{amsmath,amssymb}
\usepackage{multirow}
\usepackage{caption}
\usepackage{fancyvrb}
\usepackage{mathptmx}
\usepackage{alltt}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{lineno,hyperref}

\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
%\usepackage[thinlines]{easytable}
\captionsetup{font=footnotesize}

\modulolinenumbers[3]
\doublespacing

%\journal{Decision Support Systems}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\author{
    \IEEEauthorblockN{\normalsize Ehsan Khosrowshahi Asl\IEEEauthorrefmark{1}, Babak Khosravifar\IEEEauthorrefmark{1}, Jamal Bentahar\IEEEauthorrefmark{1}, Hadi Otrok\IEEEauthorrefmark{2}, Rabeb Mizouni\IEEEauthorrefmark{2}}\\
    \IEEEauthorblockA{\IEEEauthorrefmark{1}Concordia Institute for Information Systems Engineering, Concordia University, Montreal, Canada}
    \\
    \IEEEauthorblockA{\IEEEauthorrefmark{2}Department of Electrical and Computer Engineering, KUSTAR, Abu Dhabi, UAE}
}
\title{Distributed Decision Making for Dynamic Formation of Web Services Communities}

\begin{document}
\maketitle

\begin{abstract}
Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, existing community models mostly focus on short term goals. Moreover, these models generally suffer from high computational complexity, which makes decision making about community formation in real-time extremely hard, time consuming, and even impossible in some complex cases. In this paper, we propose a strategic distributed decision making mechanism called DDM that regulates web service agents' decision making process, which is about deciding with whom to cooperate. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our model helps 1) communities of web services efficiently find the appropriate web service to invite as new member; and 2) single web services find best communities to join. After being trained, web services get to compute expectations as utilities they would gain if cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated initiated by a web service. In general, DDM equips web services with efficient methods of foreseeing how their choices of actions would impact their short-term and long-term goals, therefore opting for better decisions. We performed experiments using real data from 142 users on 4,532 web services on 64 different time slots. The experimental results, show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.
\end{abstract}
\begin{IEEEkeywords}
Web services; Community of services; Distributed Decision Making;
\end{IEEEkeywords}

\linenumbers
\maketitle

\section{Introduction}

\IEEEPARstart{O}{ver} the past years, online services have become an important part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue. One practical solution towards delivering high quality services is utilizing intelligent decision making agents. These agents aim at maximizing their gain by exploring the best ways to provide services that satisfy end users\cite{Zeng:2003:QDW:775152.775211, 10.1109/ARES.2008.7, Demirkan2013412, journals/tsc/ZhengZYB13, Josang:2007:STR:1225318.1225716}. However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided. Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals. In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals. To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionalities but distinct nonfunctional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}. A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

@@

\begin{table*}[ht]
\caption{An example of $gain$ matrix for 3 different communities and their combinations} % title of Table
\centering % used for centering table
{\renewcommand{\arraystretch}{1.2}
\begin{tabular}{c|c c c c c c} % centered columns (4 columns)
\hline\hline %inserts double horizontal lines
 & \textless348\textgreater & \textless1934\textgreater & \textless2117\textgreater & \textless348, 1934\textgreater & \textless1934, 2117\textgreater & \textless348, 1934, 2117\textgreater \\ [0.5ex] % inserts table
%heading
\hline % inserts single horizontal line
\textless348\textgreater & - & 0.282708 & 1.027081 & 0.282708 & 18.027081 & 18.027081 \\
\textless1934\textgreater & -2.637483 & - & 6.969072 & -2.637483 & 5.509583 & 4.387725 \\
\textless2117\textgreater & 5.027081 & 2.969072 & - & 5.509583 & 2.969072 & 5.509583 \\
\textless348, 1934\textgreater & 0.0 & 0.0 & -3.851432 & - & -3.851432 & -3.851432 \\
\textless1934, 2117\textgreater & 2.969072 & 0.0 & 0.0 & 2.969072 & - & 2.969072 \\
\textless348, 1934, 2117\textgreater & 0.0 & 0.0 & 0.0 & 0.0 & 0.0 & - \\ [1ex] % [1ex] adds vertical space
\hline %inserts single line
\end{tabular}
}
\label{table:nonlin} % is used to refer this table in the text
\end{table*}

@@

\bibliographystyle{elsarticle-num} 
\bibliography{Ehsan}

\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.
